% Don't touch this %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage[left=1in,top=1in,right=1in,bottom=1in,headheight=3ex,headsep=3ex]{geometry}
\usepackage{graphicx}
\usepackage{float}

\newcommand{\blankline}{\quad\pagebreak[2]}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Modify Course title, instructor name, semester here %%%%%%%%

\title{Data 9: Sports Data Science}
\author{Daniel del Carpio}
\date{Fall, 2018}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't touch this %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[sc]{mathpazo}
\linespread{1.05} % Palatino needs more leading (space between lines)
\usepackage[T1]{fontenc}
\usepackage[mmddyyyy]{datetime}% http://ctan.org/pkg/datetime
\usepackage{advdate}% http://ctan.org/pkg/advdate
\newdateformat{syldate}{\twodigit{\THEMONTH}/\twodigit{\THEDAY}}
\newsavebox{\MONDAY}\savebox{\MONDAY}{Mon}% Mon
\newcommand{\week}[1]{%
%  \cleardate{mydate}% Clear date
% \newdate{mydate}{\the\day}{\the\month}{\the\year}% Store date
  \paragraph*{\kern-2ex\quad #1, \syldate{\today} - \AdvanceDate[4]\syldate{\today}:}% Set heading  \quad #1
%  \setbox1=\hbox{\shortdayofweekname{\getdateday{mydate}}{\getdatemonth{mydate}}{\getdateyear{mydate}}}%
  \ifdim\wd1=\wd\MONDAY
    \AdvanceDate[7]
  \else
    \AdvanceDate[7]
  \fi%
}
\usepackage{setspace}
\usepackage{multicol}
%\usepackage{indentfirst}
\usepackage{fancyhdr,lastpage}
\usepackage{url}
\pagestyle{fancy}
\usepackage{hyperref}
\usepackage{lastpage}
\usepackage{amsmath}
\usepackage{layout}

\lhead{}
\chead{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Modify header here %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\rhead{\footnotesize Text in header}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Don't touch this %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}

\usepackage{array, xcolor}
\usepackage{color,hyperref}
\definecolor{clemsonorange}{HTML}{EA6A20}
\hypersetup{colorlinks,breaklinks,linkcolor=clemsonorange,urlcolor=clemsonorange,anchorcolor=clemsonorange,citecolor=black}

\begin{document}

\maketitle

\blankline

\begin{tabular*}{.93\textwidth}{@{\extracolsep{\fill}}lr}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Modify information %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
E-mail: \texttt{ddelcarpio@berkeley.edu} \\

 Office Hours: M 10-11:45am  &  Class Hours: T/Th 3-4:15pm \\

 Office: D 609 & Class Room: Data 9 Lounge \\
 & \\
Lab Room: D 906 & Lab Hours: W 3-5pm \\
&  \\
\hline
\end{tabular*}

\vspace{5 mm}

% First Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Course Description}

This course is an introductory course on data science in sports. We will learn about how to collect sports data and use it to our advantage.

\bigskip

\noindent This course is an introductory course and does not require any specific knowledge on computer programming or sports in general. Although some programming experience and knowledge of sports will be helpful. 

% Second Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Required Materials}

\begin{itemize}
\item You will need access to a computer for this course, the textbook is online so you will not need to purchase one. 
\end{itemize}

% Third Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Prerequisites}
Prerequisites: This is an introductory course so there are no prerequisites.

% Fifth Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Course Structure}

\subsection*{Midterms}

This course will be comprised of 3 midterms, each worth 20\% of your final grade.

\subsubsection*{Lecture}
Lectures will be given on a chalkboard, and will not be webcasted. So you must come to lecture. 

\subsubsection*{Lab}
This course requires a 2-hour lab each week, you will be able to choose your lab section after the first week of class.

\subsubsection*{Final Exam and Class Project}

The final exam will be 30\% of your final grade. There is no class project for this class, your grade will only depend on how you do on exams and the final. 

\subsection*{Grading Policy}
The typical NC State grading scale will be used. I reserve the right to curve the scale dependent on overall class scores at the end of the semester. Any curve will only ever make it easier to obtain a certain letter grade. The grade will count the assessments using the following proportions:
\begin{itemize}
	\item \underline{\textbf{30\%}} of your grade will be determined by your final.
	\item \underline{\textbf{20\%}} of your grade will be determined by Midterm 1.
	\item \underline{\textbf{20\%}} of your grade will be determined by Midterm 2.
    \item \underline{\textbf{20\%}} of your grade will be determined by Midterm 3.
	\item \underline{\textbf{10\%}} of your grade will be determined by homework.

\end{itemize}


% Fifth Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section*{Course Policies}

\subsection*{During Class}
\footnotesize{I understand that the electronic recording of notes will be important for class and so computers will be allowed in class. Please refrain from using computers for anything but activities related to the class. Phones are prohibited as they are rarely useful for anything in the course. Eating and drinking are allowed in class but please refrain from it affecting the course. Try not to eat your lunch in class as the classes are typically active.}

\subsection*{Attendance Policy}
\footnotesize{Attendance is expected in all lecture and lab sections. Valid excuses for absence will be accepted before class. In extenuating circumstances, valid excuses with proof will be accepted after class. }

\subsection*{Late Assignments}
\footnotesize{Late assignments will be accepted for no penalty. If it gets to me before the final class deadline, I will see it as on time.}

\subsection*{Academic Integrity and Honesty}
\footnotesize{Students are required to comply with the university policy on academic integrity found in the Code of Student Conduct.}

\subsection*{Accommodations for Disabilities}
\footnotesize{Reasonable accommodations will be made for students with verifiable disabilities.}

\subsection*{Discrimination}
\footnotesize{Discrimination based on race, color, religion, creed, sex, national origin, age, disability, veteran status, or sexual orientation is a violation of state and federal law and/or UC Berkeley policy and will not be tolerated. Harassment of any person (either in the form of quid pro quo or creation of a hostile environment) based on race, color, religion, creed, sex, national origin, age, disability, veteran status, or sexual orientation also is a violation of state and federal.}

% Course Schedule %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section*{Schedule and weekly learning goals}

The schedule is tentative and subject to change.

% Set first date of the semester (for some reason this is a week before what comes up, but that's easy to get around)
\SetDate[01/01/2018]
\week{Week 01} Hello Python


\week{Week 02} Tables


\week{Week 03} Visualization


\week{Week 04} Basic Applications and \textbf{Midterm 1}


\week{Week 05} Simulations


\week{Week 06} Models


\week{Week 07} A/B Testing


\week{Week 08} Distributions and \textbf{Midterm 2}


\week{Week 09} Spring Break

\week{Week 10} Residuals


\week{Week 11} Classifiers 


\week{Week 12} Case Study


\week{Week 13} More Case Studies

\week{Week 14} Privacy and Ethics


\week{Week 15} Review and \textbf{Midterm 3 }

\week{Week 16} Review

\week{Week 17} \textbf{Final Exam}

\end{document}


© 2017 GitHub, Inc.
Terms
Privacy
Security
Status
Help
Contact GitHub
API
Training
Shop
Blog
